\section{Introduction}
From job matching to multiple object tracking (MOT),  matching problems can represent various decision-making applications.
A matching problem is generally described on a bipartite graph, a graph that has two sets of nodes $A$ and $B$ with edges $E=A\times B$ ($N=|A|$, $M=|B|$, $N\geq M$).
On the graph, the task is to find a matching $m$ (a set of edges that do not share any nodes) that maximally satisfies an objective.
The most famous objective is to maximize the sum of edge weights in $m$, which can be solved by the Hungarian algorithm \cite{kuhn1955hungarian}. This problem is called {\it one-sided} because only one stakeholder dominates both sides $A$ and $B$. In contrast, {\it two-sided matching} supposes that agents on each side aim to maximize their reward.

%
%A matching $m$ is a subset of $E$ whose edges do not share any nodes (see the black edges in Fig. \ref{fig:stable_matching} for an example).

A fairer two-sided matching solver provides more agreeable social decisions, but some fairness objectives make the problem {\it strongly NP-hard} \cite{kato1993complexity,mcdermid2014sex}.
Besides, agents may randomly appear/disappear in dynamic matching problems (e.g., MOT with occlusions \cite{MOT_match}).
In such cases, we need to compensate for the inputs of incomplete information by its stochastic properties.
A learning-based model can be an alternative to hand-crafted algorithms for such applications.
However, such models are underexplored.
%and there are only a few attempts \cite{harvard2019,gibbons2019deep}, in which the models are parameter redundant and their local architecture does not encode relative difference of each matching candidates well.

This paper aims to propose an effective learning-based solver for matching problems and evaluate it on {\it strongly NP-hard} conditions of {\it fair stable matching problems}.

The contribution of this paper is four-fold:
\begin{enumerate}
%\setlength{\itemsep}{0pt}      %2. ブロック間の余白
%\setlength{\parskip}{0pt}      %4. 段落間余白．
%\setlength{\itemindent}{0pt}   %5. 最初のインデント
%\setlength{\labelsep}{3pt}     %6. item と文字の間
   \item We proposed {\it WeaveNet}, a novel neural network architecture for matching problems that largely outperforms traditional learning-based approaches.
   \item For the first time, our learning-based solver achieved a comparative performance to the state-of-the-art handcrafted algorithm of NP-hard matching problems, though it was achieved with the limited size of problem instances ($N=20,~30$).
   \item For the first time, we demonstrated the performance of a deep model unsupervisedly trained by a continuous relaxation of discrete conditions of matching problems.
   %We train a deep model by continuous relaxation of conditions on matching problems and demonstrate its performance with problem instances of size $N=100$, which have never been explored.
   \item We provided a steady baseline for the problem with source code to open a new vista for learning-based combinatorial optimization\footnote{The source code and datasets are included in this submission and will be publicly available.}.
\end{enumerate}
%\sone{For the first timeが2回連続ででてくるので,はじめての表現を別にするのはどうか}

